Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-27 paper.tex
Add Component - Smart Contract

\subsubsection{smart contract}

>>>>

\subsubsection{smart contract}
Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
